The semantic drift of quotations in blogspace: a case study in short-term cultural evolution

### 2016-07-31 reviews/2016-07-response-to-reviewers.tex

\answer{
Binning is now by quantiles (makes more sense for the confidence intervals), but the extended notebooks (https://github.com/wehlutyk/brainscopypaste/tree/master/data/notebooks and https://github.com/wehlutyk/brainscopypaste/tree/master/data/figures/susceptibility.ipynb) also include graphs with the fixed-width bins we presented in the first version.
No multiple crossovers were ever observed.
}

\subsection*{Reviewer \#2}
\critique{This is a review of "How do we copy and paste? The semantic drift of quotations in blogspace." This paper attempts to discover the underlying psycholinguistic variables that is involved in blog authors making mistakes in the copying of quotations across time. Although I think the motivations and goals of this article are interesting and noteworthy, I think the actual analysis needs improvement in a number of areas.

Although I appreciate the brief writeup on intrusions in recall, the article fails to capture the amount of research done on this topic. Going back to Deese (1959; the precursor to modern experimental studies on false memory) and the subjective organization results of Tulving (1962) it has been well known that extra-list intrusions in free recall are often semantic in nature, with the intruding word being very similar in meaning to a studied item. A recent study that reinforces this is one by Zaromb, et al. (2006; JEP:LMC).
}

\answer{Thank you for these very useful and, indeed, relevant pointers.  We accordingly devoted a significant portion of the literature review to the issue of recall (see the ``Related work'' section).}

@@

\critique{ Finally, while I understand the appeal of doing a dynamic systems analysis to find the convergence points of the substitutions, but it is not really valid here.  The analysis in this paper does not provide information on what happens with multiple substitutions, so the authors cannot really make claims about the convergence points given this methodology.
}

\answer{We better explained our claims without overstating our findings.}

\critique{Overall, the analysis of the patterns of substitution in a series of quotations to validate psycholinguistic theory is novel and advances the current science.  The results would be more solid with some additional robustness checks, but in general they are quite intuitive.  I hope in the future the authors find a dataset that provides certain information about the transmission of language from one person to another, as this would allow for stronger claims about causality and greater confidence in the pattern of substitutions, as well as a finer-grained analysis of repeated substitutions.
}

\answer{On a side note, we entirely agree with the relevance of pursuing this research program in these directions, as the \emph{in vitro} observation of information transmission and its evolution is part of an ongoing project (which nonetheless remains beyond the scope of the current paper).}

### 2016-07-31 brains-protocol.tex
intermediary point

In practice \newtext{for the model first introduced above}, from the \newtext{2.60m} initial occurrences spread \tb{over} 50,427 quotation families, with significant redundancy (many quotes are indeed simple duplicates), we mine \newtext{40,868} substitutions.
From these substitutions we remove those featuring stop words, minor spelling changes (\hbox{e.g.} center/centre, November/Nov, Senator/Sen), abbreviations, spelled out numbers, \newtext{words unknown to WordNet, and deletions in substrings (which can appear as substitutions of non-deleted words)};
this eventually yields \newtext{6,318} valid substitutions \newtext{(before merging substitutions that share the same destination)}.\footnote{
\newtext{Manually coding a random subset of 100 substitutions to evaluate this last filter showed that 84 were true negatives, 5 were false positives, and 11 true positives, giving a recall score of .688.
Precision was evaluated over a random subset of 100 \emph{kept} substitutions, showing a score of .87.
Finally, note that excluding minor spelling changes does not bias our use of orthographic neighborhood density as a feature:
out of the first 100 substitutions coded for recall, those with Levenshtein distance equal to 1 (which is what orthographic neighborhood density codes,~\citealp{marian_clearpond:_2012}) were all typos or UK/US spelling changes, neither of which are relevant for this study.}
}

@@

We say that a word is \emph{substitutable} if it appears in a quote which undergoes a substitution, whether the substitution operates on that word or on another one.
\newtext{For a given group of words $g$, say all nouns, or all words in a particular range of values for a feature (\hbox{e.g.} words 2 to 4 letters long), susceptibility is computed as the ratio of $s_g$, the number of times words of that group are substituted, to $s_g^0$, the number of times words of that group would be substituted if substitutions fell randomly on substitutable words.
That is:}\footnote{
\newtext{$s_g^0$ is computed by summing, over all quotes undergoing a substitution, the ratio of the number of words in a quote that are from group $g$ to the number of words in the same quote that could have been the substitution's target.
If, for instance, half the content words of a given quote are nouns, such a quote contributes .5 to the total $s_{nouns}^0$.}
}
$$\sigma_g = \frac{s_g}{s_g^0}$$

In other words, susceptibility measures \newtext{how much more or less a group of words $g$ actually gets substituted compared to picking targets at random in quotes undergoing substitutions}.
\newtext{By applying this measure to Part-of-Speech (POS) categories and feature bins (\hbox{e.g.} for a feature $\phi$ and a bin $[a, b]$, $g = \{w | \phi(w) \in [a, b]\}$), susceptibility measures the bias in} the selection of start words involved in substitutions, \newtext{that is} the effect of word \newtext{properties} at the moment preceding the substitution when it is not yet known which word in the quotation will be substituted.\footnote{
\newtext{To avoid possible autocorrelation effects due to substitutions belonging to the same cluster (which are likely not statistically independent and may lead to overly optimistic confidence intervals), we scale $s_g$ and $s_g^0$ to count one for each cluster.
That is, each individual substitution contributes to $s_g$ or $s_g^0$ by only 1 over the number of substitutions in its cluster.}
}

>>>>

In practice \newtext{for the model first introduced above}, from the \newtext{2.60m} initial occurrences spread \tb{over} 50,427 quotation families, with significant redundancy (many quotes are indeed simple duplicates), we mine \newtext{40,868} substitutions.
From these substitutions we remove those featuring stop words, minor spelling changes (\hbox{e.g.} center/centre, November/Nov, Senator/Sen), abbreviations, spelled out numbers, \newtext{words unknown to WordNet, and deletions in substrings (which can appear as substitutions of non-deleted words)};
this eventually yields \newtext{6,318} valid substitutions\footnote{
\newtext{Manually coding a random subset of 100 substitutions to evaluate this last filter showed that 84 were true negatives, 5 were false positives, and 11 true positives, giving a recall score of .688.
Precision was evaluated over a random subset of 100 \emph{kept} substitutions, showing a score of .87.
Finally, note that excluding minor spelling changes does not bias our use of orthographic neighborhood density as a feature:
out of the first 100 substitutions coded for recall, those with Levenshtein distance equal to 1 (which is what orthographic neighborhood density codes,~\citealp{marian_clearpond:_2012}) were all typos or UK/US spelling changes, neither of which are relevant for this study.}} \newtext{\tbn{(before merging substitutions that share the same destination)}}.

@@

We say that a word is \emph{substitutable} if it appears in a quote which undergoes a substitution, whether the substitution operates on that word or on another one.
\newtext{For a given group of words $g$, say all nouns, or all words in a particular range of values for a feature (\hbox{e.g.} words 2 to 4 letters long), susceptibility is computed as the ratio of $s_g$, the number of times words of that group are substituted, to $s_g^0$, the number of times words of that group would be substituted if substitutions fell randomly on substitutable words.
That is:}\footnote{
\newtext{$s_g^0$ is computed by summing, over all quotes undergoing a substitution, the ratio of the number of words in a quote that are from group $g$ to the number of words in the same quote that could have been the substitution's target.
If, for instance, half the content words of a given quote are nouns, such a quote contributes .5 to the total $s_{nouns}^0$.} \tb{Further, t}o avoid possible autocorrelation effects due to substitutions belonging to the same cluster (which are likely not statistically independent and may lead to overly optimistic confidence intervals), we scale $s_g$ and $s_g^0$ to count one for each cluster.
That is, each individual substitution contributes to $s_g$ or $s_g^0$ by only 1 over the number of substitutions in its cluster.}
}
$$\sigma_g = \frac{s_g}{s_g^0}$$

In other words, susceptibility measures \newtext{how much more or less a group of words $g$ actually gets substituted compared to picking targets at random in quotes undergoing substitutions}.
\newtext{By applying this measure to Part-of-Speech (POS) categories and feature bins (\hbox{e.g.} for a feature $\phi$ and a bin $[a, b]$, $g = \{w | \phi(w) \in [a, b]\}$), susceptibility measures the bias in} the selection of start words involved in substitutions, 
\tb{\hbox{i.e.} it measures the preferential selection of some word properties given a substitution.}
%\newtext{that is} the effect of word \newtext{properties} at the moment preceding the substitution when it is not yet known which word in the quotation will be substituted.
